Reflections on reflection for \\ intuitionistic set theories

### 2019-01-10 paper-reflection.tex
typo

To ensure both addendum~(1) and addendum~(2), we redeclare~$S \defeq \bigcup_{k
\in \NN} P^\omega(S_k')$, where~$P^\omega(X) \defeq \bigcup_{\ell \in \NN}
P^{(\ell)}(X)$ is the union of iterated powersets.

@@

To ensure that~$H'$ is transitive and closed under subsets, we simply pass
first to its transitive closure and then compute the union of all its
finitely-iterated powersets.

@@

We set~$S \defeq \bigcup \bigl(\bigcup_{k \in \NN} f(k)\bigr)$. This set~$S$
has the required property; to verify this, it is useful to observe that
given~$u_1,\ldots,u_n \in S$, there exists a common number~$k$ such
that~$u_1,\ldots,u_n \in H$ for some~$H \in f(k)$.

>>>>

To ensure both addendum~(1) and addendum~(2), we redeclare~$S \defeq \bigcup_{k
\in \NN} P^\omega(S_k^t)$, where~$P^\omega(X) \defeq \bigcup_{\ell \in \NN}
P^{(\ell)}(X)$ is the union of iterated powersets.

@@

To ensure that~$H'$ is transitive and closed under subsets, we pass
first to its transitive closure and then compute the union of all its
finitely-iterated powersets.

@@

We set~$S \defeq \bigcup \bigl(\bigcup_{k \in \NN} f(k)\bigr)$. This set~$S$
has the required property; to verify this, it is useful to observe that
given~$u_1,\ldots,u_n \in S$, there exists a common number~$k$ such
that~$u_1,\ldots,u_n \in H$ for some~$H \in f(k)$.
% XXX
